Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-15 writeup/conStruct.tex
final changes

Another way to describe the practical significance of additional layers
is to calculate each layer's relative contribution to total covariance, 
and to choose a value of $K$ where all layers have a contribution above some cutoff (e.g. 0.1\%).
The Dirichlet prior on admixture proportions
is quite harsh against intermediate admixture values (see Table \ref{tab:param_prior_tab}),  
encouraging the model to ``not use" unnecessary layers if they are present, 
so that they will have a low contribution to overall covariance.

To calculate layer contributions, we use the following alternative description of our covariance model:
the genomes of any pair of individuals \emph{agree} with some background probability,
but this probability of agreement is increased on any segment of genome 
that both have inherited through the same layer 
(the amount it increases depends on how far apart they are.)
We use this characterization to quantify the relative contributions of each layer,
by computing the average contribution to increased probability of agreement
as described in Appendix \secref{layer_contribution}). 
This layer contribution is similar to the ``ancestry contribution'' proposed by \cite{fastStructure}. 
However, each of our layers can induce a different amount of covariance between samples embedded in them, 
so we take that into account when calculating each layer's contribution to the whole.

>>>>

Another way to describe the practical significance of additional layers
is to calculate each layer's relative contribution to total covariance, 
and to choose a value of $K$ where all layers have a contribution above some cutoff (e.g. 0.1\%).
The Dirichlet prior on admixture proportions
is quite harsh against intermediate admixture values (see Table \ref{tab:param_prior_tab}),  
encouraging the model to ``not use" unnecessary layers if they are
present \gc{in the model'}, 
so that they will have a low contribution to overall covariance.

To calculate layer contributions, we use the following alternative description of our covariance model:
the genomes of any pair of individuals \emph{agree} with some
background probability \gc{at a locus},
but this probability of agreement is increased on any segment of genome 
that both have inherited \gc{from} the same layer 
(the amount it increases depends on how far apart they are
\gc{geographically and the decay of IBD}.)
We use this characterization to quantify the relative contributions of each layer,
by computing the average contribution to increased probability of agreement
as described in Appendix \secref{layer_contribution}). 
This layer contribution is similar to the ``ancestry contribution'' proposed by \cite{fastStructure}. 
However, each of our layers can induce a different amount of covariance between samples embedded in them, 
so we take that into account when calculating each layer's contribution to the whole.
